---
title: 'S09_W2 Assignment: MUST Visit Place in Taipei for Traveler'
author: "Kieso Jan"
date: "12/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment Instructions

1. Create a web page using R Markdown that features a map created with Leaflet. 
2. Host your webpage on either GitHub Pages, RPubs, or NeoCities.  
3. Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. 

## Review criteria
The rubric contains the following two questions:

1. Does the web page feature a date and is this date less than two months before the date that you're grading this assignment?
2. Does the web page feature an interactive map that appears to have been created with Leaflet?
  
## Map
Hover to the spots and click to the website of these places! 

```{r, echo = F}  

library(leaflet)  

TPEPlace <- data.frame(lat = c(25.034640020383485, 25.03781041581507, 25.040491473724845, 25.102403961415703),
                       lng = c(121.5645883276415, 121.50060005862542, 121.56072159510262,121.54902893973286))
tourSites <- c(
  "<a href='https://https://www.taipei-101.com.tw/tw/'>Taipei 101</a>",
  "<a href='https://www.lungshan.org.tw/'>Lungshan Temple</a>",
  "<a href='https://www.yatsen.gov.tw/en/'>National Dr. Sun Yat-Sen Memorial Hall</a>",
  "<a href='https://https://www.npm.gov.tw/?l=2'>National National Palace Museum</a>"
)

#m <- leaflet() %>% addTiles() %>% setView(lng = 25.039, lat = 121.513, zoom = 18) 

TPEPlace %>% leaflet() %>% addTiles() %>%  addMarkers(popup = tourSites)

```