---
title: "S07_W4_Assignment - Building Regression Models with the mtcars Dataset"
output: 
    pdf_document :
    fig_width: 7
    fig_height: 6
    fig_caption: true
---

# Instructions

You work for Motor Trend, a magazine about the automobile industry. Looking at a data set of a collection of cars, they are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions:

  1.Is an automatic or manual transmission better for MPG    
  2.Quantify the MPG difference between automatic and manual transmissions

# Data

```{r}

data("mtcars") 

```

# Analysis

Environment Setup

```{r results='hide', message=FALSE}

library(ggplot2)
library(dbplyr)
library(tidyverse)
```


Exploratory Data Analyses

Since the main interest is to understand the relationship between transmission and MPG, isolate the two variables for exploratory data analysis

```{r echo=TRUE}

mpgAm <- mtcars %>% select(mpg, am) %>% mutate(am = as.factor(am))
ggplot(data = mpgAm, aes(x = am, y = mpg)) +
  geom_boxplot() + geom_point() +
  xlab('Transmission (0 = automatic, 1 = manual)') + 
  ylab('Miles/(US) gallon') 
```
From the box plot, it seems that manual transmission has higher mean of miles per gallon.

# Fitting Models and Model Selection

First fit all variables to mpg and look at the diagnostics to decide which ones to remove (set type-I error at 5%)

```{r echo=TRUE}

raw <- mtcars %>% mutate(cyl = as.factor(cyl), vs = as.factor(vs), am = as.factor(am), gear = as.factor(gear), carb = as.factor(carb))
fitAll <- lm(mpg ~ ., data = raw)
summary(fitAll)$coef[, 4]

```
None of the coefficients has a p-value less than 5% in the full model, indicateing that variables should be selected - by slowly removing the most insignificant variables and refitting each time

```{r echo=TRUE}

which.max(summary(fitAll)$coef[, 4]) #the cyl variable (cyl8 is the least significant)

```

```{r echo=TRUE}

fitRaw <- raw %>% select(-cyl); fitRm <- lm(mpg ~ ., data = fitRaw); summary(fitRm)$coef[, 4]

```
Again, there are no coefficients with a significant p-value after removing the cyl variable. The next most insignificant varible is removed and this process is repeated until all coefficients are significant


```{r echo=TRUE}

#which.max(summary(fitRm)$coef[, 4]) #the carb variable
fitRaw <- fitRaw %>% select(-carb); fitRm <- lm(mpg ~ ., data = fitRaw)
#summary(fitRm)$coef[, 4]; which.max(summary(fitRm)$coef[, 4]) #the gear variable
fitRaw <- fitRaw %>% select(-gear); fitRm <- lm(mpg ~ ., data = fitRaw)
#summary(fitRm)$coef[, 4]; which.max(summary(fitRm)$coef[, 4]) #the vs variable
fitRaw <- fitRaw %>% select(-vs); fitRm <- lm(mpg ~ ., data = fitRaw)
#summary(fitRm)$coef[, 4]; which.max(summary(fitRm)$coef[, 4]) #the drat variable
fitRaw <- fitRaw %>% select(-drat); fitRm <- lm(mpg ~ ., data = fitRaw)
#summary(fitRm)$coef[, 4]; which.max(summary(fitRm)$coef[, 4]) #the disp variable
fitRaw <- fitRaw %>% select(-disp); fitRm <- lm(mpg ~ ., data = fitRaw)
#summary(fitRm)$coef[, 4]; which.max(summary(fitRm)$coef[, 4]) #the hp variable
fitRaw <- fitRaw %>% select(-hp); fitRm <- lm(mpg ~ ., data = fitRaw)
summary(fitRm)$coef[, 4]

```
Finally, after removing all the variables with insignificant p-values, three coefficients, wt (wieght of 1000 lbs), qseq (1/4 mile time), and am (Transmission), have p-values less than 0.05. The porperties of this model is further explored

```{r echo=TRUE}
summary(fitRm)
```

This model indicates that given a fixed weight and 1/4 mile time, the mpg of an automatic is 9.6178 miles/gallon, but increases to 9.6178 + 2.9358 = 12.5536 miles/gallon for a manual. In addition, the adusted R-squared for this model is 0.8336, and the p-value for this model is 1.21e-11, indicating that we fail to reject the null hypothesis, and conclude that there is a significant relationship between the variables and mpg

# Diagnostics


```{r echo=TRUE}
par(mfrow = c(2, 2))
plot(fitRm)
```

The QQ plot shows a pretty good correlation of the standardized and theoretical residuals. There also doesn’t seem to be any significant patterns in the other three plots, indicating a good fit of the selected model

# Conclusions

Going back to the questions: understanding the relationship between transmission and mpg. From the model, we can conclude that when the weight and 1/4 mile time are the same for two cars, and one is an automatic and the other manual, the manual one will have an average of 2.9358 higher miles/gallon than the automatic car. Perhaps that’s why a lot of race cars are manual?



